Seasonality in governing submesoscale dynamics in the Kuroshio Extension

### 2016-07-04 writeup/rocha_etal.tex
Updates stratification figure

Figure \ref{figS2_1} shows a comparison between potential density sections
at 165$^\circ$E from
the Roemmich-Gilson Argo Climatology \citep[updated from][]{roemmich_gilson2009}.
and the LLC2160 and LLC4320 simulations. Of course, the Argo climatology is smoother
owing to lower resolution and long-term averaging. Nonetheless, simulations reproduce well the strong
seasonality in the stratification. The upper ocean is weakly stratified in late winter/early fall
and restratifies in summer. Argo climatology and LLC simulations mixed-layer depths are consistent
at all seasons (not shown).

\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=1.\textwidth]{figs/fig_s2_1.pdf}
  \caption{Potential density: a comparison between Roemmich-Gilson Argo
          climatology (a, b) and the LLC simulations 1/24$^\circ$ (c, d)
          and  1/48$^\circ$ (e, f). \textcolor{red}{Need to re-plot  the 1/24$^\circ$
          figures once extraction (currently down) becomes available}.}
  \label{figS2_1}
  \end{center}
\end{figure*}

>>>>

Figure \ref{figS2_1} shows a comparison between potential density sections
at 165$^\circ$E from
the Roemmich-Gilson Argo Climatology \citep[updated from][]{roemmich_gilson2009}.
and the LLC2160 and LLC4320 simulations. Of course, the Argo climatology is smoother
owing to lower resolution and long-term averaging. Nonetheless, simulations reproduce well the strong
seasonality in the stratification. The upper ocean is weakly stratified in late winter/early fall
and re-stratifies in summer. Argo climatology and LLC simulations mixed-layer depths are consistent
at all seasons (not shown).

\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=1.\textwidth]{figs/fig_s2_1.pdf}
  \caption{Potential density: a comparison between Roemmich-Gilson Argo
          climatology (a, b) and the LLC simulations 1/24$^\circ$ (c, d)
          and  1/48$^\circ$ (e, f).}
  \label{figS2_1}
  \end{center}
\end{figure*}
